Manuscript

### 2018-12-18 manuscript.Rmd
added g2p lin/non-g2p lin analyses

g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_druggenes
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

# Filter drug screen datasets for G2P drug-gene associations
ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

@@

## Lineage-agnostic

### Mut

@@

ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("`Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
ctrp_mut_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_mut_summ$p ~ ctrp_mut_summ$InG2P)
ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))

@@

```{r fig.height=5, fig.width=12}
plot_p_point <- ggplot(data = g2p_mut_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

```{r, eval=FALSE}
plot_p_point <- ggplot(data = g2p_mut_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

### GE

#### Pearson

@@

#### Spearman

@@

### CN

#### Pearson

@@

## Lineage-grouped

### Mut: Grid

@@

### GE/CN: G2P

@@

### GE/CN: Grid

@@

## Mut/GE/CN

### Lineage-agnostic

@@

#### CRISPR

@@

#### CCLE

@@

#### CTRP

@@

#### GDSC

@@

#### Drug: Mut

@@

all_mut_summ_plot <- ggplot(data = subset(all_res_mut, p < 0.05)) +
  facet_grid(~ Dataset) +
  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 12, by = 2), labels = seq(0, 12, by = 2)) +
  scale_x_continuous(breaks = seq(0, 0.1, by = 0.1), labels = seq(0, 0.1, by = 0.1)) +
  coord_cartesian(xlim = c(0, 0.05)) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), nudge_x = 0.05, direction = "y", hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
  labs(y = "-log10(p-value)")
all_mut_summ_plot

@@

#### Drug: GE and CN

@@

#### Drug: P-values

@@

#### Summary stats

```{r}
# Mutation status
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
g2p_druggene_all_summ_stats$n_true <- TRUE
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)

# Pearson correlations
g2p_mut_cor_stats <- g2p_mut_cor
g2p_mut_cor_stats$n_true <- TRUE
g2p_mut_cor_stats <- g2p_mut_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
          ge_mean = round(mean(Pearson_GE_Abs), 5),
          ge_sd = round(sd(Pearson_GE_Abs), 5),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          ge_n_sig_perc = ge_n_signif / ge_n * 100,
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 5),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
          cn_n_sig_perc = cn_n_signif / cn_n * 100)
```

#### CTRP example derivation

@@

### Lineage-grouped

Deriving n for Bonferroni correction:
```{r}
ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
ttest_summ_res_mut$Metric <- "Mutation Status"
mut_alphas <- ttest_summ_res_mut %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
mut_alphas$alpha_adj <- 0.05 / mut_alphas$n

ttest_summ_res_ge <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
ttest_summ_res_ge$Metric <- "Gene Expression"
ge_alphas <- ttest_summ_res_ge %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
ge_alphas$alpha_adj <- 0.05 / ge_alphas$n

ttest_summ_res_cn <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
ttest_summ_res_cn$Metric <- "Copy Number"
cn_alphas <- ttest_summ_res_cn %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
cn_alphas$alpha_adj <- 0.05 / cn_alphas$n

ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
```

Faceted lineage summaries:
```{r fig.height=4, fig.width=12}
ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
  facet_grid(Metric ~ Dataset) +
  geom_histogram(bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1), expand = c(0.01, 0.01)) +
  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank()) +
  labs(x = "P-value", y = "Frquency")
ttest_mut_summ_facet

@@

Stacked lineage summaries:
```{r fig.height=7, fig.width=12}
# plot.margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")

ttest_mut_summ_plot <- ggplot(data = dgl_mut_g2p_grid_ttest_res_list, aes(x = p_value)) +
  geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), expand = c(0.01, 0.01)) +
  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank(), panel.grid.minor.x = element_blank(), plot.margin = unit(c(30, 5.5, 1, 5.5), "pt")) +
  labs(x = "P-value", y = "Frquency", title = "Mutation status")

@@

# BOXPLOTS

@@

# CRISPR: POINT MUT MAPPING

>>>>

g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_druggenes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_druggenes, "_", fixed = TRUE), function(x) x[1]))
g2p_druggenes
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

# Filter drug screen datasets for G2P drug-gene associations
ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

@@

# PANCANCER

## Mut

@@

ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
ctrp_mut_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_mut_summ$p ~ ctrp_mut_summ$InG2P)
ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))

@@

```{r fig.height=5, fig.width=12}
plot_p_point <- ggplot(data = g2p_mut_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  geom_text_repel(data = subset(g2p_mut_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

```{r, eval=FALSE}
plot_p_point <- ggplot(data = g2p_mut_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

## GE

### Pearson

@@

### Spearman

@@

## CN

### Pearson

@@

# BY LINEAGE

## Mut: Grid

@@

## GE/CN: G2P

@@

## GE/CN: Grid

@@

# MUT/GE/CN

## Pancancer

@@

@@

@@

@@

@@

### Drug: Mut

@@

all_mut_summ_plot <- ggplot(data = subset(all_mut_res, p < 0.05)) +
  facet_grid(~ Dataset) +
  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 12, by = 2), labels = seq(0, 12, by = 2)) +
  scale_x_continuous(breaks = seq(0, 0.1, by = 0.1), labels = seq(0, 0.1, by = 0.1)) +
  coord_cartesian(xlim = c(0, 0.05)) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), nudge_x = 0.05, direction = "y", hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
  labs(y = "-log10(p-value)")
all_mut_summ_plot

@@

### Drug: GE and CN

@@

### Drug: P-values

@@

### Summary stats

```{r}
# Mutation status
g2p_mut_all_summ_stats <- g2p_mut_all_summ
g2p_mut_all_summ_stats$n_true <- TRUE
g2p_mut_all_summ_stats <- g2p_mut_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)

# Pearson correlations
g2p_cor_stats <- g2p_cor
g2p_cor_stats$n_true <- TRUE
g2p_cor_stats <- g2p_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
          ge_mean = round(mean(Pearson_GE_Abs), 5),
          ge_sd = round(sd(Pearson_GE_Abs), 5),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          ge_n_sig_perc = ge_n_signif / ge_n * 100,
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 5),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
          cn_n_sig_perc = cn_n_signif / cn_n * 100)
```

### CTRP example derivation

@@

## By lineage

### Kolmogorov-Smirnov tests

```{r}
MakeCorrResSummaryTable <- function(df_list, dataset_name) {
  res_full <- data.frame(matrix(ncol = 8, nrow = 0))
  for(i in 1:length(df_list)) {
    corr_res <- df_list[[i]] %>% group_by(G2P_DGL) %>% summarize(Dataset = dataset_name,
                Drug_Gene = names(df_list)[i],
                Lineages = paste(as.character(unique(group_general_lineage_name)), collapse = ", "),
                N_Lineages = length(as.character(unique(group_general_lineage_name))),
                Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate)
    corr_res <- merge(corr_res, compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, data = df_list[[i]], group.by = "G2P_DGL", method = "wilcox.test")[, c("G2P_DGL", "p")], by = "G2P_DGL", all = TRUE)
    corr_res$Mut_Signif <- ifelse(corr_res$p < 0.05, 1, 0)
    res_full <- rbind(res_full, corr_res)
  }
  return(res_full)
}
```

```{r}
ccle_data_g2p$G2P_DGL <- ifelse(ccle_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
ccle_data_g2p_split <- split(ccle_data_g2p, f = ccle_data_g2p$Drug_Gene)
ccle_corr_all <- MakeCorrResSummaryTable(ccle_data_g2p_split, dataset_name = "CCLE")

ctrp_data_g2p$G2P_DGL <- ifelse(ctrp_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
ctrp_data_g2p_split <- split(ctrp_data_g2p, f = ctrp_data_g2p$Drug_Gene)
ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_data_g2p_split, dataset_name = "CTRP")

gdsc_data_g2p$G2P_DGL <- ifelse(gdsc_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
gdsc_data_g2p_split <- split(gdsc_data_g2p, f = gdsc_data_g2p$Drug_Gene)
gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_data_g2p_split, dataset_name = "GDSC")

g2p_corr_all <- rbind(ccle_corr_all, ctrp_corr_all, gdsc_corr_all)
```

```{r}
G2PCorr_KStest <- function(dataset, dataset_name) {
  Metric <- colnames(dataset)[6:9]
  D_stat <- NULL
  pval <- NULL
  signif <- NULL

  yes <- dataset[dataset$G2P_DGL == "Yes",]
  no <- dataset[dataset$G2P_DGL == "No",]

  for(i in 6:9) {
    # print(yes[[colnames(yes)[i]]])
    # print(no[[colnames(no)[i]]])
    test <- ks.test(yes[[colnames(yes)[i]]], no[[colnames(no)[i]]])
    D_stat <- c(D_stat, test$statistic)
    pval <- c(pval, test$p.value)
    signif <- c(signif, ifelse(test$p.value < 0.001, "***", ifelse(test$p.value < 0.01, "**", ifelse(test$p.value < 0.05, "*", NA))))
  }
  df <- data.frame(Metric, D_stat, pval, signif)
  df$Dataset <- dataset_name
  return(df)
}
```

```{r}
ccle_corr_stats <- G2PCorr_KStest(ccle_corr_all, "CCLE")
ctrp_corr_stats <- G2PCorr_KStest(ctrp_corr_all, "CTRP")
gdsc_corr_stats <- G2PCorr_KStest(gdsc_corr_all, "GDSC")
g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
g2p_corr_stats

g2p_mut_stats <- g2p_corr_all %>% group_by(Dataset, G2P_DGL) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif),
                                                                                                   Total_Tests = length(Mut_Signif),
                                                                                                   Perc_Signif = N_Signif_Muts / Total_Tests * 100)
g2p_mut_stats
```

### Grid t-test summaries

Faceted lineage summaries:
```{r fig.height=4, fig.width=12}
ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
ttest_summ_res_mut$Metric <- "Mutation Status"

ttest_summ_res_ge <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
ttest_summ_res_ge$Metric <- "Gene Expression"

ttest_summ_res_cn <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
ttest_summ_res_cn$Metric <- "Copy Number"

ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))

ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
  facet_grid(Metric ~ Dataset) +
  geom_histogram(bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1), expand = c(0.01, 0.01)) +
  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank()) +
  labs(x = "P-value", y = "Frquency")
ttest_mut_summ_facet

@@

Stacked lineage summaries:
```{r fig.height=7, fig.width=12}
# plot.margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
ttest_mut_summ_plot <- ggplot(data = dgl_mut_g2p_grid_ttest_res_list, aes(x = p_value)) +
  geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), expand = c(0.01, 0.01)) +
  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank(), panel.grid.minor.x = element_blank(), plot.margin = unit(c(30, 5.5, 1, 5.5), "pt")) +
  labs(x = "P-value", y = "Frquency", title = "Mutation status")

@@

# OLD: BOXPLOTS

@@

# OLD: CRISPR POINT MUT MAPPING
